Plots for Latent Hawkes Paper

### 2020-11-24 output_scripts/Paper_Plots.Rmd
update plots to deal with pair wise intensities

load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
load(paste(sim_data_path,"fit123_state_est.RData",sep=''))

@@

    ## Posterior density
    current_result <- eval(parse(text=paste("sim_model3_stan_sim",m,sep="")))
    for(i in c(1:n_sim)){
      lines(density(current_result[[i]]$f[1001:2000,j]),
            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
    }

@@

test.mmhp <- sim_model3_data[plot.s][[1]]$mmhp_matrix[plot.i,plot.j][[1]]
temp.t <- test.mmhp$tau
current.n <- length(temp.t)-1
time.segment <- seq(0,tail(temp.t,1),length.out=5000)

### Preprocess the model inference result
## model 1
#########
model1_par_est <- list(lambda0 =
                         mean(sim_model3_stan_sim1[[plot.s]]$lambda0[1001:2000]),
                       eta_1=mean(sim_model3_stan_sim1[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model3_stan_sim1[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model3_stan_sim1[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model3_stan_sim1[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model3_stan_sim1[[plot.s]]$f[1001:2000,],2,mean))
lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
                                                   model1_par_est$lambda0,
                                    alpha =
                                      model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                    model1_par_est$f[plot.j],
                                    model1_par_est$eta_1,
                                    model1_par_est$eta_2,
                                    model1_par_est$eta_3),
                                    beta=model1_par_est$beta),
                                     events=temp.t,
                                     time.vec=time.segment)

## model2
#############
model2_par_est <- list(gamma=apply(sim_model3_stan_sim2[[plot.s]]$gamma[1001:2000,],
                                   2,mean),
                    zeta = 
                      apply(sim_model3_stan_sim2[[plot.s]]$zeta[1001:2000,],2,mean),
                       eta_1=mean(sim_model3_stan_sim2[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model3_stan_sim2[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model3_stan_sim2[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model3_stan_sim2[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model3_stan_sim2[[plot.s]]$f[1001:2000,],2,mean))

## Model3
#############
mmhp_par_est <- list(lambda0=mean(sim_model3_stan_sim3[[plot.s]]$lambda0[1001:2000]),
                     lambda1=mean(sim_model3_stan_sim3[[plot.s]]$lambda1[1001:2000]),
                     eta_1=mean(sim_model3_stan_sim3[[plot.s]]$eta_1[1001:2000]),
                     eta_2=mean(sim_model3_stan_sim3[[plot.s]]$eta_2[1001:2000]),
                     eta_3=mean(sim_model3_stan_sim3[[plot.s]]$eta_3[1001:2000]),
                     beta=mean(sim_model3_stan_sim3[[plot.s]]$beta[1001:2000]),
                     f=apply(sim_model3_stan_sim3[[plot.s]]$f[1001:2000,],2,mean))

object_hat <- list(lambda0=mmhp_par_est$lambda0,
                   lambda1=mmhp_par_est$lambda1,
                   alpha=model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
                                             mmhp_par_est$f[cur_j],
                                             mmhp_par_est$eta_1,
                                             mmhp_par_est$eta_2),
                   beta=mmhp_par_est$beta,
                   q1=model3_fn$q1.fun(mmhp_par_est$f[cur_i],
                                       mmhp_par_est$f[cur_j],
                                       mmhp_par_est$eta_3),
                   q2=model3_fn$q0.fun(mmhp_par_est$f[cur_i],
                                       mmhp_par_est$f[cur_j],
                                       mmhp_par_est$eta_3))

state.est.latent.mmhp <- interpolate_state_est_lst[[plot.s]][plot.i,plot.j][[1]]
state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
                                                 termination=200)

lambda.m3 <- mmhpIntensityNumeric(params=object_hat,
                                  t=temp.t[-1],
                                  time.vec=time.segment,
                                  latent.vec=step.fun.est(time.segment))

@@

lambda.true <- mmhpTrueIntensityNumeric(params=object_true,
                                        t=temp.t,
                       latent=list(x=fixStateTransition(test.mmhp)$x,
                              z=fixStateTransition(test.mmhp)$z),
                              time.vec=time.segment)

@@

```{r fig4b-recover-latent-states,fig.width=8,fig.height=4}
y.ub <- c(17,17,17)#c(130,72,31)
x_events <- 135#150
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 140#160#200#130
my.long.x <- 140#205#134.5
legend.x <- c(50,50,50)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(15,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

@@

@@

    ## Posterior density
    current_result <- eval(parse(text=paste("sim_model1_stan_sim",
                                            m,
                                            "_total",
                                            sep="")))
    for(i in c(1:n_sim)){
      lines(density(current_result[[i]]$f[1001:2000,j]),
            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
    }

@@

    ## Posterior density
    current_result <- eval(parse(text=paste("sim_model2_stan_sim",
                                            m,
                                            "_total",
                                            sep="")))
    for(i in c(1:n_sim)){
      lines(density(current_result[[i]]$f[1001:2000,j]),
            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
    }

@@

load(paste0(m1_path,m1_files[plot.s]))

@@

### Preprocess the model inference result
## model 1
#########
model1_par_est <- list(lambda0 =
                         mean(sim_model1_stan_sim1_total[[plot.s]]$lambda0[1001:2000]),
                       eta_1=mean(sim_model1_stan_sim1_total[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model1_stan_sim1_total[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model1_stan_sim1_total[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model1_stan_sim1_total[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model1_stan_sim1_total[[plot.s]]$f[1001:2000,],2,mean))
lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
                                                   model1_par_est$lambda0,
                                    alpha =
                                      model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                    model1_par_est$f[plot.j],
                                    model1_par_est$eta_1,
                                    model1_par_est$eta_2,
                                    model1_par_est$eta_3),
                                    beta=model1_par_est$beta),
                                     events=temp.t,
                                     time.vec=time.segment)

## model2
#############
model2_par_est <- list(gamma=apply(sim_model1_stan_sim2_total[[plot.s]]$gamma[1001:2000,],
                                   2,mean),
                    zeta = 
                      apply(sim_model1_stan_sim2_total[[plot.s]]$zeta[1001:2000,],2,mean),
                       eta_1=mean(sim_model1_stan_sim2_total[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model1_stan_sim2_total[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model1_stan_sim2_total[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model1_stan_sim2_total[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model1_stan_sim2_total[[plot.s]]$f[1001:2000,],2,mean))

@@

## Model3
#############
mmhp_par_est <- list(lambda0=mean(sim_model1_stan_sim3_total[[plot.s]]$lambda0[1001:2000]),
                     lambda1=mean(sim_model1_stan_sim3_total[[plot.s]]$lambda1[1001:2000]),
                     eta_1=mean(sim_model1_stan_sim3_total[[plot.s]]$eta_1[1001:2000]),
                     eta_2=mean(sim_model1_stan_sim3_total[[plot.s]]$eta_2[1001:2000]),
                     eta_3=mean(sim_model1_stan_sim3_total[[plot.s]]$eta_3[1001:2000]),
                     beta=mean(sim_model1_stan_sim3_total[[plot.s]]$beta[1001:2000]),
                     f=apply(sim_model1_stan_sim3_total[[plot.s]]$f[1001:2000,],2,mean))

object_hat <- list(lambda0=mmhp_par_est$lambda0,
                   lambda1=mmhp_par_est$lambda1,
                   alpha=model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
                                             mmhp_par_est$f[cur_j],
                                             mmhp_par_est$eta_1,
                                             mmhp_par_est$eta_2),
                   beta=mmhp_par_est$beta,
                   q1=model3_fn$q1.fun(mmhp_par_est$f[cur_i],
                                       mmhp_par_est$f[cur_j],
                                       mmhp_par_est$eta_3),
                   q2=model3_fn$q0.fun(mmhp_par_est$f[cur_i],
                                       mmhp_par_est$f[cur_j],
                                       mmhp_par_est$eta_3))

@@

@@

```{r fig 4b M1 sim}
source(here("lib","mod_drawHawkesIntensityPaper.R"))
y.ub <- c(17,17,17)#c(130,72,31)
x_events <- 135#150
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 140#160#200#130
my.long.x <- 140#205#134.5
legend.x <- c(50,50,50)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(15,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

@@

@@

load(paste0(m2_path,m2_files[plot.s]))

@@

### Preprocess the model inference result
## model 1
#########
model1_par_est <- list(lambda0 =
                         mean(sim_model2_stan_sim1_total[[plot.s]]$lambda0[1001:2000]),
                       eta_1=mean(sim_model2_stan_sim1_total[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model2_stan_sim1_total[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model2_stan_sim1_total[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model2_stan_sim1_total[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model2_stan_sim1_total[[plot.s]]$f[1001:2000,],2,mean))
lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
                                                   model1_par_est$lambda0,
                                    alpha =
                                      model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                    model1_par_est$f[plot.j],
                                    model1_par_est$eta_1,
                                    model1_par_est$eta_2,
                                    model1_par_est$eta_3),
                                    beta=model1_par_est$beta),
                                     events=temp.t,
                                     time.vec=time.segment)

## model2
#############
model2_par_est <- list(gamma=apply(sim_model2_stan_sim2_total[[plot.s]]$gamma[1001:2000,],
                                   2,mean),
                    zeta = 
                      apply(sim_model2_stan_sim2_total[[plot.s]]$zeta[1001:2000,],2,mean),
                       eta_1=mean(sim_model2_stan_sim2_total[[plot.s]]$eta_1[1001:2000]),
                       eta_2=mean(sim_model2_stan_sim2_total[[plot.s]]$eta_2[1001:2000]),
                       eta_3=mean(sim_model2_stan_sim2_total[[plot.s]]$eta_3[1001:2000]),
                       beta=mean(sim_model2_stan_sim2_total[[plot.s]]$beta[1001:2000]),
                       f=apply(sim_model2_stan_sim2_total[[plot.s]]$f[1001:2000,],2,mean))

## Model3
#############
mmhp_par_est <- list(lambda0=mean(sim_model2_stan_sim3_total[[plot.s]]$lambda0[1001:2000]),
                     lambda1=mean(sim_model2_stan_sim3_total[[plot.s]]$lambda1[1001:2000]),
                     eta_1=mean(sim_model2_stan_sim3_total[[plot.s]]$eta_1[1001:2000]),
                     eta_2=mean(sim_model2_stan_sim3_total[[plot.s]]$eta_2[1001:2000]),
                     eta_3=mean(sim_model2_stan_sim3_total[[plot.s]]$eta_3[1001:2000]),
                     beta=mean(sim_model2_stan_sim3_total[[plot.s]]$beta[1001:2000]),
                     f=apply(sim_model2_stan_sim3_total[[plot.s]]$f[1001:2000,],2,mean))

object_hat <- list(lambda0=mmhp_par_est$lambda0,
                   lambda1=mmhp_par_est$lambda1,
                   alpha=model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
                                             mmhp_par_est$f[cur_j],
                                             mmhp_par_est$eta_1,
                                             mmhp_par_est$eta_2),
                   beta=mmhp_par_est$beta,
                   q1=model3_fn$q1.fun(mmhp_par_est$f[cur_i],
                                       mmhp_par_est$f[cur_j],
                                       mmhp_par_est$eta_3),
                   q2=model3_fn$q0.fun(mmhp_par_est$f[cur_i],
                                       mmhp_par_est$f[cur_j],
                                       mmhp_par_est$eta_3))

>>>>

# load(paste(sim_data_path,"sim_model3_fit123.RData",sep=''))
# load(paste(sim_data_path,"fit123_state_est.RData",sep=''))
#### need to edit here to account for separate files now

m3_files <- list.files(sim_data_path, pattern = "sim_model3_fit*")
#m1_files

# load(paste0(m1_path,m1_files[1]))
sim_model3_stan_sim1_total <- list()
sim_model3_stan_sim2_total <- list()
sim_model3_stan_sim3_total <- list()

for(i in seq_along(m3_files)) {
  load(paste0(sim_data_path,m3_files[i]))
  sim_model3_stan_sim1_total[[i]] <- sim_model3_stan_sim1
  sim_model3_stan_sim2_total[[i]] <- sim_model3_stan_sim2
  sim_model3_stan_sim3_total[[i]] <- sim_model3_stan_sim3

@@

    ## Posterior density
    # current_result <- eval(parse(text=paste("sim_model3_stan_sim",m,sep="")))
    current_result <- eval(parse(text=paste("sim_model3_stan_sim",
                                            m,
                                            "_total",
                                            sep="")))
    for(i in c(1:n_sim)){
      lines(density(current_result[[i]]$f[,j]),
            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
    }

@@

load(paste0(sim_data_path, "sim_model3_",
                               plot.s,
                              ".RData"))
test.mmhp <- sim_model3_data$mmhp_matrix[plot.i,plot.j][[1]]
temp.t <- test.mmhp$tau
current.n <- length(temp.t)-1
time.segment <- seq(0, tail(temp.t,1), length.out = 5000)

### Preprocess the model inference result
## model 1
#########
model1_par_est <- list(lambda0 = mean(sim_model3_stan_sim1_total[[plot.s]]$lambda0),
                       eta_1 = mean(sim_model3_stan_sim1_total[[plot.s]]$eta_1),
                       eta_2 = mean(sim_model3_stan_sim1_total[[plot.s]]$eta_2),
                       eta_3 = mean(sim_model3_stan_sim1_total[[plot.s]]$eta_3),
                       beta = mean(sim_model3_stan_sim1_total[[plot.s]]$beta),
                       f = apply(sim_model3_stan_sim1_total[[plot.s]]$f, 2, mean))
lambda.m1<-uniHawkesIntensityNumeric(object = list(lambda0 = 
                                                   model1_par_est$lambda0,
                                    alpha =
                                      model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                    model1_par_est$f[plot.j],
                                    model1_par_est$eta_1,
                                    model1_par_est$eta_2,
                                    model1_par_est$eta_3),
                                    beta = model1_par_est$beta),
                                     events = temp.t,
                                     time.vec = time.segment)

## model2
#############
model2_par_est <- list(gamma = apply(sim_model3_stan_sim2_total[[plot.s]]$gamma,
                                     2, mean),
                    zeta = apply(sim_model3_stan_sim2_total[[plot.s]]$zeta, 2, mean),
                    eta_1 = mean(sim_model3_stan_sim2_total[[plot.s]]$eta_1),
                    eta_2 = mean(sim_model3_stan_sim2_total[[plot.s]]$eta_2),
                    eta_3 = mean(sim_model3_stan_sim2_total[[plot.s]]$eta_3),
                    beta = mean(sim_model3_stan_sim2_total[[plot.s]]$beta),
                    f = apply(sim_model3_stan_sim2_total[[plot.s]]$f, 2, mean))

lambda.m2 <- uniHawkesIntensityNumeric(object=list(
  lambda0 = model2_par_est$gamma[plot.i]+
          model2_par_est$zeta[plot.j],                                        
  alpha = model1_fn$alpha.fun(model2_par_est$f[plot.i],
                            model2_par_est$f[plot.j],
                            model2_par_est$eta_1,
                            model2_par_est$eta_2,
                            model2_par_est$eta_3),
                beta = model2_par_est$beta),
                events = temp.t,
                time.vec = time.segment)

## Model3
###
lam0_vec <- apply(sim_model3_stan_sim3_total[[plot.s]]$lambda0, 2, mean)
lam1_vec <- apply(sim_model3_stan_sim3_total[[plot.s]]$lambda1, 2, mean)
lam0_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
                       ncol = length(object_par$f_vec_1))
lam1_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
                       ncol = length(object_par$f_vec_1))

clean_sim_data <- cleanSimulationData(raw_data = sim_model3_data, 
                                      cut_off = cut_off,
                                      N = length(object_par$f_vec_1))

for(i in seq_along(lam0_vec)) {
  row_id <- clean_sim_data$I_fit[i]
  col_id <- clean_sim_data$J_fit[i]
  lam0_par_est[row_id, col_id] <- lam0_vec[i]
  lam1_par_est[row_id, col_id] <- lam1_vec[i]
}

###

#############
mmhp_par_est <- list(lambda0 = lam0_par_est,
                     lambda1 = lam1_par_est,
                     eta_1 = mean(sim_model3_stan_sim3_total[[plot.s]]$eta_1),
                     eta_2 = mean(sim_model3_stan_sim3_total[[plot.s]]$eta_2),
                     eta_3 = mean(sim_model3_stan_sim3_total[[plot.s]]$eta_3),
                     beta = mean(sim_model3_stan_sim3_total[[plot.s]]$beta),
                     f = apply(sim_model3_stan_sim3_total[[plot.s]]$f,2,mean))

object_hat <- list(lambda0 = mmhp_par_est$lambda0[cur_i, cur_j],
                   lambda1 = mmhp_par_est$lambda1[cur_i, cur_j],
                   alpha = model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
                                             mmhp_par_est$f[cur_j],
                                             mmhp_par_est$eta_1,
                                             mmhp_par_est$eta_2),
                   beta = mmhp_par_est$beta,
                   q1 = model3_fn$q1.fun(mmhp_par_est$f[cur_i],
                                       mmhp_par_est$f[cur_j],
                                       mmhp_par_est$eta_3),
                   q2=model3_fn$q0.fun(mmhp_par_est$f[cur_i],
                                       mmhp_par_est$f[cur_j],
                                       mmhp_par_est$eta_3))

## then need to load in the state estimate here
load(paste0(sim_data_path, "fit123_state_est_", plot.s, ".RData"))

step.fun.est <- stepfun(state.est.latent.mmhp$x.hat,
                        2 - state.est.latent.mmhp$z.hat)

lambda.m3 <- mmhpIntensityNumeric(params = object_hat,
                                  t = temp.t[-1],
                                  time.vec = time.segment,
                                  latent.vec = step.fun.est(time.segment))

@@

lambda.true <- mmhpTrueIntensityNumeric(params = object_true,
                                        t = temp.t,
                       latent = list(x = fixStateTransition(test.mmhp)$x,
                                     z = fixStateTransition(test.mmhp)$z),
                                     time.vec = time.segment)

@@

```{r fig4b-recover-latent-states,fig.width=8,fig.height=4}
y.ub <- c(3,3,3)#c(130,72,31)
x_events <- 135#150
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 140#160#200#130
my.long.x <- 140#205#134.5
legend.x <- c(30,30,30)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(2.5,2,2)#c(15,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

legend(legend.x[2]-20,
       legend.y[2]+2,c("State 0/1 events","State change point"),
       col = c(NA,"red"),
       y.intersp=0.85,x.intersp=-0.1, bty = "n",
       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
       lty = c(NA,NA), lwd=c(NA,4))
points(14,8+2,pch=1,cex=2,col="blue")
points(16,8+2,pch=16,cex=2,col="blue")

@@

legend(legend.x[1]-20,legend.y[3],c("Overestimation","Underestimation"),
       col = c(positive.col,negative.col),
       y.intersp=0.88,x.intersp=0.5,bty = "n",
       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)

@@

    ## Posterior density
    current_result <- eval(parse(text=paste("sim_model1_stan_sim",
                                            m,
                                            "_total",
                                            sep="")))
    for(i in c(1:n_sim)){
      lines(density(current_result[[i]]$f[,j]),
            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
    }

@@

    ## Posterior density
    current_result <- eval(parse(text=paste("sim_model2_stan_sim",
                                            m,
                                            "_total",
                                            sep="")))
    for(i in c(1:n_sim)){
      lines(density(current_result[[i]]$f[,j]),
            col=add.alpha(model_colors[m], alpha=0.8),cex=0.6,lwd=0.8)
    }

@@

load(paste0(m1_path,m1_files[plot.s]))
clean_sim_data_m1 <- cleanSimulationData(raw_data = sim_model1_data[[1]], 
                                      cut_off = cut_off,
                                      N = length(object_par$f_vec_1))
# this loads in sim data too

@@

### Preprocess the model inference result
## model 1
#########
model1_par_est <- list(lambda0 = 
                         mean(sim_model1_stan_sim1_total[[plot.s]]$lambda0),
                   eta_1 = mean(sim_model1_stan_sim1_total[[plot.s]]$eta_1),
                   eta_2 = mean(sim_model1_stan_sim1_total[[plot.s]]$eta_2),
                   eta_3 = mean(sim_model1_stan_sim1_total[[plot.s]]$eta_3),
                   beta = mean(sim_model1_stan_sim1_total[[plot.s]]$beta),
                   f = apply(sim_model1_stan_sim1_total[[plot.s]]$f,2,mean))
lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
                                                   model1_par_est$lambda0,
                                    alpha =
                                    model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                    model1_par_est$f[plot.j],
                                    model1_par_est$eta_1,
                                    model1_par_est$eta_2,
                                    model1_par_est$eta_3),
                                    beta=model1_par_est$beta),
                                    events=temp.t,
                                    time.vec=time.segment)

## model2
#############
model2_par_est <- list(gamma = apply(sim_model1_stan_sim2_total[[plot.s]]$gamma,
                                   2,mean),
                       zeta = apply(sim_model1_stan_sim2_total[[plot.s]]$zeta,
                                  2, mean),
                     eta_1 = mean(sim_model1_stan_sim2_total[[plot.s]]$eta_1),
                     eta_2 = mean(sim_model1_stan_sim2_total[[plot.s]]$eta_2),
                     eta_3 = mean(sim_model1_stan_sim2_total[[plot.s]]$eta_3),
                     beta = mean(sim_model1_stan_sim2_total[[plot.s]]$beta),
                     f = apply(sim_model1_stan_sim2_total[[plot.s]]$f, 
                             2, mean))

@@

## Model3
#############
####
lam0_vec <- apply(sim_model1_stan_sim3_total[[plot.s]]$lambda0, 2, mean)
lam1_vec <- apply(sim_model1_stan_sim3_total[[plot.s]]$lambda1, 2, mean)
lam0_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
                       ncol = length(object_par$f_vec_1))
lam1_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
                       ncol = length(object_par$f_vec_1))

### loaded in sim data again above

for(i in seq_along(lam0_vec)) {
  row_id <- clean_sim_data_m1$I_fit[i]
  col_id <- clean_sim_data_m1$J_fit[i]
  lam0_par_est[row_id, col_id] <- lam0_vec[i]
  lam1_par_est[row_id, col_id] <- lam1_vec[i]
}
####
mmhp_par_est <- list(lambda0 = lam0_par_est,
                     lambda1 = lam1_par_est,
                     eta_1 = mean(sim_model1_stan_sim3_total[[plot.s]]$eta_1),
                     eta_2 = mean(sim_model1_stan_sim3_total[[plot.s]]$eta_2),
                     eta_3 = mean(sim_model1_stan_sim3_total[[plot.s]]$eta_3),
                     beta = mean(sim_model1_stan_sim3_total[[plot.s]]$beta),
                     f = apply(sim_model1_stan_sim3_total[[plot.s]]$f, 2, mean))

object_hat <- list(lambda0 = mmhp_par_est$lambda0[cur_i, cur_j],
                   lambda1 = mmhp_par_est$lambda1[cur_i, cur_j],
                   alpha = model3_fn$alpha.fun(mmhp_par_est$f[cur_i],
                                             mmhp_par_est$f[cur_j],
                                             mmhp_par_est$eta_1,
                                             mmhp_par_est$eta_2),
                   beta = mmhp_par_est$beta,
                   q1 = model3_fn$q1.fun(mmhp_par_est$f[cur_i],
                                       mmhp_par_est$f[cur_j],
                                       mmhp_par_est$eta_3),
                   q2 = model3_fn$q0.fun(mmhp_par_est$f[cur_i],
                                       mmhp_par_est$f[cur_j],
                                       mmhp_par_est$eta_3))

@@

state.est.latent.mmhp <- interpolate_state_est_lst[plot.i,plot.j][[1]]
state.est.latent.mmhp.new <- fixInterpolateState(state.est.latent.mmhp,
                                                 termination = 200)

@@

```{r fig 4b M1 sim}
source(here("lib","mod_drawHawkesIntensityPaper.R"))
y.ub <- c(27,27,27)#c(130,72,31)
x_events <- 135#150
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 140#160#200#130
my.long.x <- 140#205#134.5
legend.x <- c(110,110,110)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(20,20,20)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

legend(legend.x[2]-40,
       legend.y[2]+2,c("State 0/1 events","State change point"),
       col = c(NA,"red"),
       y.intersp=0.85,x.intersp=-0.1, bty = "n",
       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
       lty = c(NA,NA), lwd=c(NA,4))
points(legend.x[2]-35,16,pch=1,cex=2,col="blue")
points(legend.x[2]-34,16,pch=16,cex=2,col="blue")

@@

legend(legend.x[3]-40,
       legend.y[3],c("Overestimation","Underestimation"),
       col = c(positive.col,negative.col),
       y.intersp=0.88,x.intersp=0.5,bty = "n",
       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)

@@

load(paste0(m2_path,m2_files[plot.s]))
clean_sim_data_m2 <- cleanSimulationData(raw_data = sim_model2_data[[1]], 
                                      cut_off = cut_off,
                                      N = length(object_par$f_vec_1))

@@

### Preprocess the model inference result
## model 1
#########
model1_par_est <- list(lambda0 = mean(sim_model2_stan_sim1_total[[plot.s]]$lambda0),
                       eta_1 = mean(sim_model2_stan_sim1_total[[plot.s]]$eta_1),
                       eta_2 = mean(sim_model2_stan_sim1_total[[plot.s]]$eta_2),
                       eta_3 = mean(sim_model2_stan_sim1_total[[plot.s]]$eta_3),
                       beta = mean(sim_model2_stan_sim1_total[[plot.s]]$beta),
                       f = apply(sim_model2_stan_sim1_total[[plot.s]]$f,2,mean))
lambda.m1<-uniHawkesIntensityNumeric(object=list(lambda0 = 
                                                   model1_par_est$lambda0,
                                    alpha =
                                      model1_fn$alpha.fun(model1_par_est$f[plot.i],
                                    model1_par_est$f[plot.j],
                                    model1_par_est$eta_1,
                                    model1_par_est$eta_2,
                                    model1_par_est$eta_3),
                                    beta=model1_par_est$beta),
                                     events=temp.t,
                                     time.vec=time.segment)

## model2
#############
model2_par_est <- list(gamma = apply(sim_model2_stan_sim2_total[[plot.s]]$gamma,
                                   2,mean),
                    zeta = apply(sim_model2_stan_sim2_total[[plot.s]]$zeta,2,mean),
                    eta_1 = mean(sim_model2_stan_sim2_total[[plot.s]]$eta_1),
                    eta_2 = mean(sim_model2_stan_sim2_total[[plot.s]]$eta_2),
                    eta_3 = mean(sim_model2_stan_sim2_total[[plot.s]]$eta_3),
                    beta = mean(sim_model2_stan_sim2_total[[plot.s]]$beta),
                    f = apply(sim_model2_stan_sim2_total[[plot.s]]$f, 2, mean))

lambda.m2 <- uniHawkesIntensityNumeric(object=list(
  lambda0 = model2_par_est$gamma[plot.i]+
          model2_par_est$zeta[plot.j],                                        
  alpha = model1_fn$alpha.fun(model2_par_est$f[plot.i],
                            model2_par_est$f[plot.j],
                            model2_par_est$eta_1,
                            model2_par_est$eta_2,
                            model2_par_est$eta_3),
                beta = model2_par_est$beta),
                events = temp.t,
                time.vec = time.segment)

## Model3
#############
lam0_vec <- apply(sim_model2_stan_sim3_total[[plot.s]]$lambda0, 2, mean)
lam1_vec <- apply(sim_model2_stan_sim3_total[[plot.s]]$lambda1, 2, mean)

lam0_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
                       ncol = length(object_par$f_vec_1))
lam1_par_est <- matrix(0, nrow = length(object_par$f_vec_1),
                       ncol = length(object_par$f_vec_1))

for(i in seq_along(lam0_vec)) {
  row_id <- clean_sim_data_m2$I_fit
  col_id <- clean_sim_data_m2$J_fit
  lam0_par_est[row_id, col_id] <- lam0_vec[i]
  lam1_par_est[row_id, col_id] <- lam1_vec[i]
}

mmhp_par_est <- list(lambda0 = lam0_par_est,
                     lambda1 = lam1_par_est,
                     eta_1 = mean(sim_model2_stan_sim3_total[[plot.s]]$eta_1),
                     eta_2 = mean(sim_model2_stan_sim3_total[[plot.s]]$eta_2),
                     eta_3 = mean(sim_model2_stan_sim3_total[[plot.s]]$eta_3),
                     beta = mean(sim_model2_stan_sim3_total[[plot.s]]$beta),
                     f = apply(sim_model2_stan_sim3_total[[plot.s]]$f,2,mean))
